Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
appendix update

# Appendix 1 - Pollster Methodology

The New York Times/Siena College Poll is a respected polling partnership that provides data-driven insights into U.S. public opinion, particularly on political, social, and economic issues. Known for its rigorous methodology, this poll focuses on capturing the views of registered and likely voters across the country, with particular emphasis on key battleground states during election cycles. The poll is frequently cited for its accuracy and transparency, and is widely regarded as reliable by the public, political analysts, and the media.

The New York Times/Siena College Poll is conducts live telephone interviews with a national sample of registered voters, using both landlines and cellphones, with over 90% of contacts made via cellphones. The sample frame is drawn from a comprehensive voter file covering 200 million registered voters. This file provides demographic and geographic information, enabling representative sampling across age, race, and political affiliation. The poll targets registered U.S. voters, with special focus on battleground states like Arizona, Georgia, Michigan, Nevada, Pennsylvania, and Wisconsin, determined as swing states. Respondents are randomly selected from the voter file, ensuring a diverse sample by region, party, and demographics. To mitigate non-response bias, the poll applies demographic weighting, increasing the weight of underrepresented groups, such as young adults or non-college graduates. Low response rates (around 2%) present challenges, to mitigate this, weighing adjustments are applied to correct for demographic imbalances and potential non-response bias. Questions are structured to be clear, neutral, and representative across political views, with each question carefully reviewed for balance and clarity. This process reduces the risk of bias in responses, though the brief format of phone surveys limits depth (@NYTpolls).

# Appendix 2 - Survey

@@

# Appendix 3- Posterior Predictive Check {#sec-checks}

>>>>

# Pollster Methodology

The New York Times/Siena College Poll is a respected polling partnership known for providing data-driven insights into U.S. public opinion on political, social, and economic issues. Recognized for its rigorous methodology, the poll focuses on capturing the views of registered and likely voters across the country, with particular emphasis on key battleground states during election cycles. Frequently cited for its accuracy and transparency, it is widely regarded as a reliable source by the public, political analysts, and the media.

The poll conducts live telephone interviews with a national sample of registered voters, reaching over 90% of respondents via cellphones. The target population consists of U.S. registered voters, with the sampling frame drawn from a comprehensive voter file covering 200 million individuals. This file contains demographic and geographic information to ensure sampling is representative across age, race, political affiliation, and region. The poll places particular focus on swing states like Arizona, Georgia, Michigan, Nevada, Pennsylvania, and Wisconsin, where small shifts in voter opinion can determine the electoral outcome. Respondents are recruited randomly from the voter file to capture a diverse range of political perspectives, demographics, and regional backgrounds. To mitigate non-response bias, which is significant given a response rate of around 2%, the poll applies demographic weighting to underrepresented groups, such as young adults and non-college graduates (@NYTpolls).

The methodology of telephone polling provides benefits, such as enabling random sampling across a broad population. However, low response rates and the shift away from landlines to cellphones mean certain groups, particularly younger adults, may be underrepresented despite demographic weighting adjustments. While the questionnaire is crafted to be clear, neutral, and balanced across political views, the brief format of phone surveys—designed to improve response rates—limits depth. Additionally, phone surveys may not reach segments of the population more responsive to digital surveys or in-person interviews, potentially missing out on specific voter perspectives. Each respondent’s answer is then adjusted for weighting to ensure proportionality, and results are aggregated to reflect a balanced, representative outcome of public opinion, rather than raw, unadjusted numbers.

Overall, while the New York Times/Siena College Poll is highly regarded for its thorough approach, methodological constraints, such as low response rates and limited outreach to digitally-focused populations, introduce challenges to representativeness.

# Survey

@@

# Posterior Predictive Check {#sec-checks}
